Supporting information: Copulas and their potential for ecology

### 2019-10-07 SupportingInformation.Rmd
fig fixed: see response, please

#pdf("./Results/taylorslaw_results/SpatialTL_CNFSC_kendall.pdf",height=4,width=16)
png("./Results/taylorslaw_results/SpatialTL_CNFSC_kendall.png",width=16,height=4,units="in",res=400)
op<-op<-par(mfrow=c(1,4),mar=c(4,5,1,1),mgp=c(3,1,0))
##plot TL for clayton
plot(kend.points.res[[1]][,1,],kend.points.res[[1]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=1.5,cex.lab=1.5)  
points(kend.points.res[[1]][,1,1],kend.points.res[[1]][,2,1],type='p',pch=20,cex=.75,col='red')
points(kend.points.res[[1]][,1,2],kend.points.res[[1]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Clayton"),side = 3, line=-2, adj=0.1, col="black")

##plot TL for normal copula
plot(kend.points.res[[2]][,1,],kend.points.res[[2]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=1.5,cex.lab=1.5)  
points(kend.points.res[[2]][,1,1],kend.points.res[[2]][,2,1],type='p',pch=20,cex=.75,col='red')
points(kend.points.res[[2]][,1,2],kend.points.res[[2]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Normal"),side = 3, line=-2, adj=0.1, col="black")

#plot TL for frank
plot(kend.points.res[[3]][,1,],kend.points.res[[3]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=1.5,cex.lab=1.5)  
points(kend.points.res[[3]][,1,1],kend.points.res[[3]][,2,1],type='p',pch=20,cex=.75,col='red')
points(kend.points.res[[3]][,1,2],kend.points.res[[3]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Frank"),side = 3, line=-2, adj=0.1, col="black")

#plot TL for survival clayton
plot(kend.points.res[[4]][,1,],kend.points.res[[4]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=1.5,cex.lab=1.5)  
points(kend.points.res[[4]][,1,1],kend.points.res[[4]][,2,1],type='p',pch=20,cex=.75,col='red')
points(kend.points.res[[4]][,1,2],kend.points.res[[4]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Survival Clayton"),side=3, line=-2, adj=0.1, col="black")

@@

pdf("./Results/taylorslaw_results/SpatialTL_7stats_kendall.pdf",height=3,width=21)
op<-par(mfrow=c(1,7),mar=c(4.2,5,1,1),mgp=c(3,1,0))
#***DAN: x axis needs to be redone to show the copula names used in the surrogates

#x<-1:4
x2<-c("C", "N", "F", "SC")
#plot(x,s.lin[1,],type="l",col="grey",ylim=range(s.lin),xlab="Set of surrogates",ylab="Linearity test p-vals",
#     cex.axis=1.5,cex.lab=1.5,xaxt="n")
#points(x,s.lin[1,],col="red")
#axis(1, at = c(1:4), x2, cex.axis=1.5)
#for (counter in 2:dim(s.lin)[1]){
#  lines(x,s.lin[counter,],col="grey")
#  points(x,s.lin[counter,],col="red")
#}
boxplot(s.lin , col=rainbow(4), xlab="Copula family", ylab="Linearity test p-vals", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

#plot s.hom distr for each set of surrogates
boxplot(s.hom , col=rainbow(4), xlab="Copula family", ylab="Homoskedasticity test p-vals", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

#plot s.rmse distr for each set of surrogates
boxplot(s.rmse , col=rainbow(4) , xlab="Copula family", ylab="Spatial TL rmse", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

#plot s.int distr for each set of surrogates
boxplot(s.int , col=rainbow(4) , xlab="Copula family", ylab="Spatial TL intercept", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

#plot s.slope distr for each set of surrogates
boxplot(s.slope , col=rainbow(4) , xlab="Copula family", ylab="Spatial TL slope", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

#plot s.quadcoeff distr for each set of surrogates
boxplot(s.quadcoeff , col=rainbow(4) , xlab="Copula family", ylab="Spatial TL quadratic coefficient", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

#plot s.mncurv distr for each set of surrogates
boxplot(s.mncurv , col=rainbow(4) , xlab="Copula family", ylab="Spatial TL mean curvature", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

@@

#pdf("./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.pdf",height=4,width=16)
png("./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.png",height=4,width=16,units="in",res=400)
op<-op<-par(mfrow=c(1,4),mar=c(4,5,1,1),mgp=c(3,1,0))
##plot TL for clayton
plot(spea.points.res[[1]][,1,],spea.points.res[[1]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=1.5,cex.lab=1.5)  
points(spea.points.res[[1]][,1,1],spea.points.res[[1]][,2,1],type='p',pch=20,cex=.75,col='red')
points(spea.points.res[[1]][,1,2],spea.points.res[[1]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Clayton"),side = 3, line=-2, adj=0.1, col="black")

##plot TL for normal copula
plot(spea.points.res[[2]][,1,],spea.points.res[[2]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=1.5,cex.lab=1.5)  
points(spea.points.res[[2]][,1,1],spea.points.res[[2]][,2,1],type='p',pch=20,cex=.75,col='red')
points(spea.points.res[[2]][,1,2],spea.points.res[[2]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Normal"),side = 3, line=-2, adj=0.1, col="black")

#plot TL for frank
plot(spea.points.res[[3]][,1,],spea.points.res[[3]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=1.5,cex.lab=1.5)  
points(spea.points.res[[3]][,1,1],spea.points.res[[3]][,2,1],type='p',pch=20,cex=.75,col='red')
points(spea.points.res[[3]][,1,2],spea.points.res[[3]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Frank"),side = 3, line=-2, adj=0.1, col="black")

#plot TL for survival clayton
plot(spea.points.res[[4]][,1,],spea.points.res[[4]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=1.5,cex.lab=1.5)  
points(spea.points.res[[4]][,1,1],spea.points.res[[4]][,2,1],type='p',pch=20,cex=.75,col='red')
points(spea.points.res[[4]][,1,2],spea.points.res[[4]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Survival Clayton"),side=3, line=-2, adj=0.1, col="black")

@@

pdf("./Results/taylorslaw_results/SpatialTL_7stats_spearman.pdf",height=3,width=21)
op<-par(mfrow=c(1,7),mar=c(4.2,5,1,1),mgp=c(3,1,0))
x2<-c("C", "N", "F", "SC")

#plot s.lin distr for each set of surrogates
boxplot(s.lin , col=rainbow(4), xlab="Copula family", ylab="Linearity test p-vals", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

#plot s.hom distr for each set of surrogates
boxplot(s.hom , col=rainbow(4), xlab="Copula family", ylab="Homoskedasticity test p-vals", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

#plot s.rmse distr for each set of surrogates
boxplot(s.rmse , col=rainbow(4) , xlab="Copula family", ylab="Spatial TL rmse", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

#plot s.int distr for each set of surrogates
boxplot(s.int , col=rainbow(4) , xlab="Copula family", ylab="Spatial TL intercept", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

#plot s.slope distr for each set of surrogates
boxplot(s.slope , col=rainbow(4) , xlab="Copula family", ylab="Spatial TL slope", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

#plot s.quadcoeff distr for each set of surrogates
boxplot(s.quadcoeff , col=rainbow(4) , xlab="Copula family", ylab="Spatial TL quadratic coefficient", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

#plot s.mncurv distr for each set of surrogates
boxplot(s.mncurv , col=rainbow(4) , xlab="Copula family", ylab="Spatial TL mean curvature", cex.axis=1.5,cex.lab=1.5,xaxt="n")
axis(1, at = c(1:4), x2, cex.axis=1.5)

>>>>

#pdf("./Results/taylorslaw_results/SpatialTL_CNFSC_kendall.pdf",height=4,width=16)
png("./Results/taylorslaw_results/SpatialTL_CNFSC_kendall.png",width=16,height=4,units="in",res=400)
op<-par(mfrow=c(1,4),mar=c(8,8,2,1),mgp=c(4,1,0))
##plot TL for clayton
plot(kend.points.res[[1]][,1,],kend.points.res[[1]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3)  
points(kend.points.res[[1]][,1,1],kend.points.res[[1]][,2,1],type='p',pch=20,cex=.75,col='red')
points(kend.points.res[[1]][,1,2],kend.points.res[[1]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Clayton"),side = 3, line=-2, adj=0.1, col="black",cex=2)

##plot TL for normal copula
plot(kend.points.res[[2]][,1,],kend.points.res[[2]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3)  
points(kend.points.res[[2]][,1,1],kend.points.res[[2]][,2,1],type='p',pch=20,cex=.75,col='red')
points(kend.points.res[[2]][,1,2],kend.points.res[[2]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Normal"),side = 3, line=-2, adj=0.1, col="black",cex=2)

#plot TL for frank
plot(kend.points.res[[3]][,1,],kend.points.res[[3]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3)  
points(kend.points.res[[3]][,1,1],kend.points.res[[3]][,2,1],type='p',pch=20,cex=.75,col='red')
points(kend.points.res[[3]][,1,2],kend.points.res[[3]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Frank"),side = 3, line=-2, adj=0.1, col="black",cex=2)

#plot TL for survival clayton
plot(kend.points.res[[4]][,1,],kend.points.res[[4]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3)  
points(kend.points.res[[4]][,1,1],kend.points.res[[4]][,2,1],type='p',pch=20,cex=.75,col='red')
points(kend.points.res[[4]][,1,2],kend.points.res[[4]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Survival Clayton"),side=3, line=-2, adj=0.1, col="black",cex=2)

@@

pdf("./Results/taylorslaw_results/SpatialTL_7stats_kendall.pdf",height=3,width=22)
op<-par(mfrow=c(1,7),mar=c(8,8,2,1),mgp=c(3,1,0))
#***DAN: x axis needs to be redone to show the copula names used in the surrogates

#x<-1:4
x2<-c("C", "N", "F", "SC")
#plot(x,s.lin[1,],type="l",col="grey",ylim=range(s.lin),xlab="Set of surrogates",ylab="Linearity test p-vals",
#     cex.axis=1.5,cex.lab=1.5,xaxt="n")
#points(x,s.lin[1,],col="red")
#axis(1, at = c(1:4), x2, cex.axis=1.5)
#for (counter in 2:dim(s.lin)[1]){
#  lines(x,s.lin[counter,],col="grey")
#  points(x,s.lin[counter,],col="red")
#}
boxplot(s.lin , col=rainbow(4), xlab="Copula family", ylab="p-vals", cex.axis=2,cex.lab=3,xaxt="n")
mtext("Linearity test", side=3, cex=1.8,line=1.5)
axis(1, at = c(1:4), x2, cex.axis=2)

#plot s.hom distr for each set of surrogates
boxplot(s.hom , col=rainbow(4), xlab="Copula family", ylab="p-vals", cex.axis=2,cex.lab=3,xaxt="n")
mtext("Homoskedasticity test", side=3, cex=1.8,line=1.5)
axis(1, at = c(1:4), x2, cex.axis=2)

#plot s.rmse distr for each set of surrogates
boxplot(s.rmse , col=rainbow(4) , xlab="Copula family", ylab="rmse", cex.axis=2,cex.lab=3,xaxt="n")
mtext("Spatial TL", side=3, cex=1.8,line=1.5)
axis(1, at = c(1:4), x2, cex.axis=2)

#plot s.int distr for each set of surrogates
boxplot(s.int , col=rainbow(4) , xlab="Copula family", ylab="intercept", cex.axis=2,cex.lab=3,xaxt="n")
mtext("Spatial TL", side=3, cex=1.8,line=1.5)
axis(1, at = c(1:4), x2, cex.axis=2)

#plot s.slope distr for each set of surrogates
boxplot(s.slope , col=rainbow(4) , xlab="Copula family", ylab="slope", cex.axis=2,cex.lab=3,xaxt="n")
mtext("Spatial TL", side=3, cex=1.8,line=1.5)
axis(1, at = c(1:4), x2, cex.axis=2)

#plot s.quadcoeff distr for each set of surrogates
boxplot(s.quadcoeff , col=rainbow(4) , xlab="Copula family", ylab="quadratic \n coefficient", cex.axis=2,cex.lab=3,xaxt="n")
mtext("Spatial TL", side=3, cex=1.8,line=1.5)
axis(1, at = c(1:4), x2, cex.axis=2)

#plot s.mncurv distr for each set of surrogates
boxplot(s.mncurv , col=rainbow(4) , xlab="Copula family", ylab="mean \n curvature", cex.axis=2,cex.lab=3,xaxt="n")
mtext("Spatial TL", side=3, cex=1.8,line=1.5)
axis(1, at = c(1:4), x2, cex.axis=2)

@@

#pdf("./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.pdf",height=4,width=16)
png("./Results/taylorslaw_results/SpatialTL_CNFSC_spearman.png",height=4,width=16,units="in",res=400)
op<-par(mfrow=c(1,4),mar=c(8,8,2,1),mgp=c(4,1,0))
##plot TL for clayton
plot(spea.points.res[[1]][,1,],spea.points.res[[1]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3)  
points(spea.points.res[[1]][,1,1],spea.points.res[[1]][,2,1],type='p',pch=20,cex=.75,col='red')
points(spea.points.res[[1]][,1,2],spea.points.res[[1]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Clayton"),side = 3, line=-2.5, adj=0.1, col="black",cex=2)

##plot TL for normal copula
plot(spea.points.res[[2]][,1,],spea.points.res[[2]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3)  
points(spea.points.res[[2]][,1,1],spea.points.res[[2]][,2,1],type='p',pch=20,cex=.75,col='red')
points(spea.points.res[[2]][,1,2],spea.points.res[[2]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Normal"),side = 3, line=-2.5, adj=0.1, col="black",cex=2)

#plot TL for frank
plot(spea.points.res[[3]][,1,],spea.points.res[[3]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3)  
points(spea.points.res[[3]][,1,1],spea.points.res[[3]][,2,1],type='p',pch=20,cex=.75,col='red')
points(spea.points.res[[3]][,1,2],spea.points.res[[3]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Frank"),side = 3, line=-2, adj=0.1, col="black",cex=2)

#plot TL for survival clayton
plot(spea.points.res[[4]][,1,],spea.points.res[[4]][,2,],type='p',pch=20,cex=.75,xlim=xlimits,ylim=ylimits,
     xlab=expression(log[10]("spatial mean")),ylab=expression(log[10]("spatial variance")),
     cex.axis=2,cex.lab=3)  
points(spea.points.res[[4]][,1,1],spea.points.res[[4]][,2,1],type='p',pch=20,cex=.75,col='red')
points(spea.points.res[[4]][,1,2],spea.points.res[[4]][,2,2],type='p',pch=20,cex=.75,col='green')
mtext(paste("Survival Clayton"),side=3, line=-2.5, adj=0.1, col="black",cex=2)

@@

pdf("./Results/taylorslaw_results/SpatialTL_7stats_spearman.pdf",height=3,width=24)
op<-par(mfrow=c(1,7),mar=c(8,9,4,1),mgp=c(4,1,0))
x2<-c("C", "N", "F", "SC")

#plot s.lin distr for each set of surrogates
boxplot(s.lin , col=rainbow(4), xlab="Copula family", ylab="p-vals", cex.axis=2,cex.lab=3,xaxt="n")
mtext("Linearity test", side=3, cex=1.8,line=1.5)
axis(1, at = c(1:4), x2, cex.axis=2)

#plot s.hom distr for each set of surrogates
boxplot(s.hom , col=rainbow(4), xlab="Copula family", ylab="p-vals", cex.axis=2,cex.lab=3,xaxt="n")
mtext("Homoskedasticity test", side=3, cex=1.8,line=1.5)
axis(1, at = c(1:4), x2, cex.axis=2)

#plot s.rmse distr for each set of surrogates
boxplot(s.rmse , col=rainbow(4) , xlab="Copula family", ylab="rmse", cex.axis=2,cex.lab=3,xaxt="n")
mtext("Spatial TL", side=3, cex=1.8,line=1.5)
axis(1, at = c(1:4), x2, cex.axis=2)

#plot s.int distr for each set of surrogates
boxplot(s.int , col=rainbow(4) , xlab="Copula family", ylab="intercept", cex.axis=2,cex.lab=3,xaxt="n")
mtext("Spatial TL", side=3, cex=1.8,line=1.5)
axis(1, at = c(1:4), x2, cex.axis=2)

#plot s.slope distr for each set of surrogates
boxplot(s.slope , col=rainbow(4) , xlab="Copula family", ylab="slope", cex.axis=2,cex.lab=3,xaxt="n")
mtext("Spatial TL", side=3, cex=1.8,line=1.5)
axis(1, at = c(1:4), x2, cex.axis=2)

#plot s.quadcoeff distr for each set of surrogates
boxplot(s.quadcoeff , col=rainbow(4) , xlab="Copula family", ylab="quadratic \n coefficient", cex.axis=2,cex.lab=3,xaxt="n")
mtext("Spatial TL", side=3, cex=1.8,line=1.5)
axis(1, at = c(1:4), x2, cex.axis=2)

#plot s.mncurv distr for each set of surrogates
boxplot(s.mncurv , col=rainbow(4) , xlab="Copula family", ylab="mean \n curvature", cex.axis=2,cex.lab=3,xaxt="n")
mtext("Spatial TL", side=3, cex=1.8,line=1.5)
axis(1, at = c(1:4), x2, cex.axis=2)
